Master Thesis

### 2013-05-06 motivation.tex
Motivating IGs

However, abstract categorial grammars are quite young and no significant
grammar has been developed under this framework. To facilitate the
creation of such a grammar, we will borrow heavily from the Frigram
Interaction Grammar \cite{perrier2007french} and its linguistic
resources.

>>>>

However, abstract categorial grammars are quite young and no significant
grammar has been developed under this framework. To facilitate the
creation of such a grammar, we will borrow heavily from the Frigram
Interaction Grammar \cite{perrier2007french} and its linguistic
resources. Namely, we will rely on the fact that Frigram is defined
separately from its lexicon, Frilex, which we will use in its
entirety. Frigram, the grammar itself, can also serve us as a guideline
when designing our own grammar thanks to the close ties between the
formalisms of interaction grammars and abstract categorial grammars
\cite{perrier1999intuitionistic}.
